%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% 
%% Miguel Cabrera's resume
%%   - based off work by Michael DeCorte and Yisong Yue
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%%
%% The following code sets up the document formatting
%%

%this assumes that res_yy.sty is in some path
\documentstyle[hyperref, margin, line,textcomp]{res_yy}


%\hypersetup{pdfpagemode=Full,colorlinks=true,backref}

\addtolength{\oddsidemargin}{-0.45in}
\addtolength{\voffset}{-0.30in}
\addtolength{\textwidth}{1.00in} \addtolength{\textheight}{1.50in}

\renewcommand{\namefont}{\LARGE\emph}



%%
%% The following code defines some macros for terms which have raised font
%% (ie 4\fourth would result 4th with the 'th' raised (superscripted)
%%

\def\Cplusplus{{\rm C\raise.7ex\hbox{\scriptsize ++}}}
\def\CSharp{{\rm C\raise.7ex\hbox{\scriptsize \#}}}
% 'st' 'nd' 'rd' 'th' superscripts for numbers
\def\first{{\raise.5ex\hbox{\small st}}}
\def\second{{\raise.5ex\hbox{\small nd}}}
\def\third{{\raise.5ex\hbox{\small rd}}}
\def\fourth{{\raise.5ex\hbox{\small th}}}



%%
%% starting the actual document
%%

\begin{document}

%the name in big fonts at the top of resume
%this is left aligned
\name{Miguel Fernando Cabrera Granados}

%this is right aligned

%this is right aligned
\address {  \begin{tabular}{lllll}
  Cl 32EE \# 80 - 60 APT 402  & \ \ & (+57 4) 3509000 ext 9521 \\
  Edf. Samaria - Barrio Laureles  & \ \ & (+57 3)  300 492 8461   \\
  Medell\'{i}n - Antioquia & \ \ & mfcabrera@gmail.org \\  
  Colombia  & \ \ & http://mfcabrera.com \\
  \end{tabular}
}
\begin{resume}

%%
%% This section of code is inelegant, but I'm too lazy to fix it
%%

%% Correct this stating that IR is also important for me, not only for
% application.

\section{\textsc{Objective}}
%To work in a challenging environment and build world-class software
%solutions.
To work in a challenging enviroment using cutting-edge technologies, delivering world class software based solutions.
%My research interests lie primarily in Machine Learning and its
%applications.
%  specially but  not limited, to Information Retrieval and Filtering, Intelligent Information Systems, Recommender Systems, Desktop and Enterprise Search.

%\section{\textsc{Research\\ Interest}}
%My research interests lie primarily in Machine Learning and its application  specially but  not limited to Information Retrieval and Filtering, Intelligent Information Systems, Recommender Systems, Desktop and Enterprise Search.

\section{\textsc{Summary}}
Application developer and technology consultant with experience in a
wide range of technologies, mostly open source.


\section{\textsc{Education}}
\textbf{National University of Colombia }- Medell\'{i}n Campus \hfill 2002 - 2007 \\
{Systems and Informatic Engineer} \hfill 

%\section{\textsc{Education}}
%\textbf{Corporacion Universitaria del Caribe}  \hfill 2001 - 2003 \\
%{Systems Engineer - No Title} \hfill 
%% \section{\textsc{Course\\ Work}}
%%   \begin{tabular}{lllll}
%% Information Networks   & \ \ &  Operation Research   & \ \ &
%% Multiagent Systems  \\ 
%% Digital Image Processing     & \ \ & Complex Systems  & \ \ &
%% Declarative Languages  \\
%% Software Engineering   & \ \ & Algorithms          & \ \ & Artificial Intelligence     \\
%% Operating Systems      & \ \ & Databases I and II          & \ \ & Computer Architecture \\
%% Numerical Methods      & \ \ & Macroeconomics       & \ \ & Differential Equations      \\
%% Basic Probability      & \ \ & Microeconomics      & \ \ & Linear Algebra and Linear Systems      \\
%% Advanced Calculus      & \ \ & Linear Algebra    & \ \ & Computational Intelligence   \\
%% \end{tabular}
%%\newline

\section{\textsc{Awards}}
\textbf{Andr\'{e}s Bello Medal} \hfill          Bogota - Colombia - 2000 \\
Given by the Education Ministry to the best scores in the ICFES National pre-university exam \hfill 

\section{\textsc{Languages}}
\textbf{Spanish}\   - \  Mother tongue \\
\textbf{English}\ \  - \ Fluent \\
%\textbf{French}\ \  - \  Begginer (Level 1)
%%
%% the meat of the resume starts now
%%

\begin{formatb}
  \title{l}\employer{l}\\
 \location{r}\dates{r}\\
  \body\\
\end{formatb}

\section{\textsc{Work\\ Experience}}

\employer{\textbf{February 2008 - Present}}
\title{\textbf{Analyst} }
\location{Accenture} 
\dates{Medell\'{i}n, Colombia }
\begin{position}
Member of the system integration team for a newly acquired  trading
platform (Murex) for the Colombian largest Banking group (Bancolombia). 
My responsibilities can be summarized as:
\begin{itemize}
\item {Interaction with the stakeholders in order to extract requirements for interfacing Murex with external systems.}
\item {Interfacing bank's legacy systems and Murex using XML based technologies.}
\item {Java  based development for Interfacing  a local price system  with Murex.}
\item {Java development of the Integration layer for an external Tax module of the new trading platform.}
\end{itemize} 

This required learning concepts about  Capital markets, treasury operational model, FX products, real time
pricing and trading system technologies.

Technological tools used:
C, Java, \CSharp,Linux,AIX,IBM  Websphere MQ and Murex MX.3.

\end{position}


\employer{\textbf{March 2007 - January 2008 }}
\title{\textbf{Web Developer} }
\location{School of Systems, National University of Colombia} 
\dates{Medell\'{i}n, Colombia }
\begin{position}
Provided technical Web expertise that helped to enhance Systems School's corporate web site, 
as defined in the University's web publishing policy. Maintained and
configured the School's web servers. Developed and maintained the
staff directory, student and staff intranets which retrieved
information from MySQL databases using PHP. Implemented a MVC Based
model using Smarty templates.
%\textbf{Supervisor}:  Dr. Fernando Arnango Isaza,Ms.c, Ph.d.\\
%\textbf{Telephone}: (+57 4) 425 5362 
\end{position}

\employer{\textbf{January 2007 - May 2007}}
\title{\textbf{Research Assistant}}
\location{School of Geological Sciences, National University of Colombia}
\dates{Medell\'{i}n, Colombia}
\begin{position}
I Worked in the set-up, running and modification of the NOAA's WaveWatch III Model under a Linux based Cluster
for high performance wave height prediction on the Caribbean Sea.
%\textbf{Supervisor}:  Dr. Andr\'{e}s Osorio,Ms.c, Ph.d.\\
%\textbf{Telephone}: (+57 4) 425 5223
\end{position}


\employer{\textbf{January 2006 - December 2006}}
\title{\textbf{Open Source Engineer}}
\location{{Soluciones Kazak}}
\dates{Medell\'{i}n, Colombia}
\begin{position}
My team developed custom  Linux distribution for our client (a medium
size company, then performed a full-scale migration to Linux
(workstating and servers) using the distribution. I also worked on  the set-up of many enterprise
servers ranging from small ISP to medium size companies. 
http://www.kazak.com.co
\end{position}
\newline
\newline
\newline
\newline
\newline



\employer{\textbf{February 2005 - December 2005}}
\title{\textbf{Software Developer}}
\location{{Interplanet}}
\dates{Envigado, Colombia}
\begin{position}
My work consisted mostly  in internal development and system
 administration   for  company's information systems.
We performed modification to the Radius protocol software used inside the company.
I also worked as an outsourced software developer giving support and
 mantaining  a Web application for one of our clients.  I used Perl and C for internal
development and  system administration tasks and Java JSP/Servlet
framework for Web Application development. This work required problem
 solving skills, end-user contact and requirement taking.
%\textbf{Supervisor}:  Ing. Jaime Roldan.\\
%\textbf{Telephone}:  (+57 4) 331 0623 
\end{position}

%\newline
%\newline
%\newline
%% \newline
%% \newline
%% \newline

%\employer{\textbf{September 2003 - December 2004}}
%\title{\textbf{Server Administrator - Technical Support}}
%\location{Systems Laboratory, National University of Colombia}
%\dates{Medell\'{i}n, Colombia}
%\begin{position}
%I administered two Linux servers, which hosted the Systems School's
%cororate and staff pages.I provided support to technical problems 
%to computer rooms users and coordinated the computer room maintenance.
%\textbf{Supervisor}:  John Jairo Tabares.\\
%\textbf{Telephone}:  (+57 4) 425 5312 
%\end{position}
%\newline


%% \employer{\textbf{Interspersed 2006 and 2007}}
%% \title{\textbf{Web Developer}}
%% \location{School of Systems and Informatics, NUC}
%% \dates{Medell\'{i}n, Colombia}
%% \begin{position}
%% 2007 - 2006 Version of EITI Conference Webpage (Ecuentro De Investigaci\'{o}n Sobre Tecnologías de Informaci\'{o}n Aplicadas a las Soluci\'{o}n de Problemas).
%% \end{position}



%%
%% We use the same formatting for projects as for work experience
%% Shown below is the formatting used previously
%%
%%  \begin{formatb}
%%    \employer{l}\title{r}\\
%%    \location{l}\dates{r}\\
%%    \body\\
%%  \end{formatb}
%%
%% 
%%  Note that \location is now being used for non-location information
%%
 \begin{formatb}
   \employer{l}\dates{r}\\
   \body\\
 \end{formatb}
%% 
%% \section{\textsc{Publications}}
%% 
%% \employer{\textbf{A Support Vector Method for Optimizing Average Precision}}
%% \dates{SIGIR 2007}
%% \begin{position}
%% Authors: Yisong Yue, Thomas Finley, Filip Radlinski, Thorsten Joachims
%% \end{position}


%%
%% This section could also use more formatting, but looks ok, as is
%%

\section{\textsc{Skills}}

\emph{General}: Communication and presentation skills. Team
working. Strong technical knowledge in UN*X systems (specially Linux).

\emph{Programming Languages}: I have had working experience with
 C/\Cplusplus, Perl, SQL, Java and PHP. I have had experience with \
 \CSharp, Ruby and Python in personal projects and as Freelance.

\emph{Libraries and Tools}: Emacs, Autotools, \LaTeX, GIMP, MatLab, Eclipse, GTKSharp, GCC, GDB, Diff, Patch, SVN, CVS,JSP/Servlets, Rails.

\emph{Operating Systems}: Advanced user and administration skills in
Linux (Ubuntu,SuSE,Debian,CentOS). Knowledge of Linux internal
working, Advanced Windows user. User experience in  AIX and  other UN*X flavors.

\emph{Others}: XML,\ (X)HTML, CSS, MySQL, PosgreSQL, Oracle, UML, LyX, Apache.


\section{\textsc{Other\\  Projects}}

\employer{\textbf{Parallel Transductive SVMs for Document Classification}}
\dates{July 2007 - December 2007}
\begin{position}
We developed a paralell implementation of a transductive
linear support vector machine. The main Idea of the work was
to find out whether the parallelization of such algorithm using a cascade
setup have any influence on its performance. This was my thesis
project. I used Information Retrieval techniques in order to create
the index on which the algorithm made the classification.
\\
\textbf{Advisor}:  Dr. Jairo Espinosa, Msc,Ph.d.
\end{position}

\employer{\textbf{Web based Repository of Range Images}}
\dates{March 2006 - July 2006}
\begin{position}
 In this project I developed a Web based repository for Range Images, the goal of the
 project was to create a centralized repository for all the range
 images generated from research projects around world in the field of
 object reconstruction and surface fitting. The application was
 developed using Ruby on Rails with a MySQL database.
% \textbf{Supervisor}: Dr. John William Branch Msc,Ph.d.
\end{position}

\employer{\textbf{Beagle CHM Filter}}
\dates{May 2005 - July 2005}
\begin{position}
Beagle a Desktop search tool  for Linux similar to
Google\texttrademark  \  Desktop
Search. I developed a filter for CHM (Windows' Help format) indexing.
http://www.beagle-project.org
\end{position}

\employer{\textbf{Ubuntu and Gnome}}
\dates{2005-2006}
\begin{position}
Bug reporting (QA) and translation (English to Spanish)
\end{position}
%%
%% Note that we're redefining the formatting
%% We only have one row of information now, instead of two
%%

%% \section{\textsc{Extracurricular\\ Activities}}

%% \begin{formatb}
%%   \employer{l}
%%   \dates{r}\\
   
%%   \body\\
%% \end{formatb}

%% \employer{\textbf{UNALIX}}
%% \dates{June 2003 - January 2006}
%% \begin{position}
%% UNALIX is the University's Linux and Open Source User Group, I was one
%% of the founder member  and general coordinator until January of
%% 2006. UNALIX is both an user group and academic group where we
%% discuss the technology and the applicability of Open Source Software
%% in the University's environment. http://www.unalix.org
%% \end{position}


%% \employer{\textbf{ParqueSoft Medell\'{i}n}}
%% \dates{January 2007 -  June 2007}
%% \begin{position}
%% I am one of the founder of ParqueSoft Medell\'{i}n, A local branch of
%% ParqueSoft, a technology cluster that fosters entrepreneurship which have its 
%% main headquarters in the city of Cali.  I was part of the local directive board
%% as a representative of the entrepreneurs.
%% \end{position}

\section{\textsc{Technical \\ Talks (Given)}}

\begin{formatb}
  \employer{l}\\
  \dates{r}\location{l}\\
   \body
\end{formatb}

\employer{\textbf{Web Development for Programmers: Introduction to Ruby on Rails}}
\dates{October 2006}
\location {Universidad Distrital (District University) - Bogota, Colombia}
\begin{position}
Semana Linux Universidad Distrital (SLUD-V).
\end{position}

\employer{\textbf{Enterprise Open Source Massive Migration.}}
\dates{October 2006}
\location {Universidad Distrital (District Univeristy) - Bogota, Colombia}
\begin{position}
Semana Linux Universidad Distrital (SLUD-V).
\end{position}

\employer{\textbf{Introduction to Mono Development Environment}}
\dates{September 2005}
\location {CECAR - Sincelejo, Colombia}
\begin{position}
Software Freedom Day Celebration.
\end{position}
\newline     
\newline     
\newline     
\newline     


\section{\textsc{Organization}}
\employer{\textbf{}}
\dates{}
\textbf{III Free Software International Congress}, Organizing member. Medell\'{i}n - Colombia. April 2004.
%\begin{position}
%\end{position}

\section{\textsc{Professional\\ Memberships}}

\begin{formatb}
  \employer{l}\dates{r}\\
  \body\\
\end{formatb}
\employer{}
   {\textbf{UNALIX} - University's Linux and Open Source User Group,
     June 2003 - June 2007 (Founding member and Coordinator)\\ \\
    \textbf{Association of Computing and Machinery (ACM) Professional 
      Member} March 2005 - Present 
 

}

%\dates{}
%\begin{position}
%\end{position}


%Redefining the format
\begin{formatb}
  \employer{l}\title{r}\\
  \location{l}\dates{r}\\
 \body\\
\end{formatb}

%\section{\textsc{Teaching\\ Experience}}
%\employer{\textbf{Extension Courses Instructor}}
%\title{\textbf{June to July 2005}}
%\location{Systems Laboratory,National University of Colombia} 
%\dates{Medell\'{i}n, Colombia }
%\begin{position}
%Introduction to Web Development with PHP and MySQL extension course.
%\end{position}


%%
%% Nothing special here, just a normal table
%%

%\section{\textsc{Course Work}}
%  \begin{tabular}{lllll}
%  Information Networks   & \ \ & Machine Learning    & \ \ & Theory of Computation \\ 
%  Computer Graphics      & \ \ & Machine Vision      & \ \ & Programming Languages \\
%  Software Engineering   & \ \ & Algorithms          & \ \ & Artificial Intelligence     \\
%  Operating Systems      & \ \ & Databases           & \ \ & Computer Architecture \\
%  Numerical Methods      & \ \ & Graph Theory        & \ \ & Differential Equations      \\
%  Probability Theory     & \ \ & Number Theory       & \ \ & Differential Geometry       \\
%  Advanced Calculus      & \ \ & Abstract Algebra    & \ \ & Advanced Combinatorics   \\
%  \end{tabular}

\section{\textsc{Personal\\ Interests}}
\employer{}
\title{}
\location{} 
\dates{}
Brazilian Jiu-Jitsu, Judo, Film Critic, Web 2.0 Technologies and trends, Open Source Software, Hiking.

\section{\textsc{Referees}}


 Esteban Salazar Guzman\\
 Integration Analyst \\
 SETI S.A. \\
 Tel\'{e}fono: +57 4 321-5151 \\
 Cell: +57 3003943091 \\ 
 E-mail: estebansalazar@seti.com.co\\
 \\  
 Jairo Jos\'{e} Espinosa Msc,Phd.\\
 Associate Professor \\
 Escuela de Ingenier\'{i}a Elecrica y Mec\'{a}nica \\
 Facultad de Minas \\
 Universidad Nacional de Colombia - Sede  Medell\'{i}n\\
 Tel\'{e}fono: +57 4 4255284 \\
 E-mail: jairo.espinosa@ieee.org\\
 \\  
  Rafael Ignacio Larios\\
 Analyst  \\
 Grupo Bancolombia S.A. \\
 Tel\'{e}fono: +57 4 312-9189  \\
 E-mail: rlarios@bancolombia.com.co \\

 Andres Felipe Jimenez\\
 Senior Analyst  \\
 Accenture. \\
 Tel\'{e}fono: +57 4 3509000 ext 9521  \\
 E-mail: andres.f.jimenez@accenture.com \\

%% Ing. Jairo Jos\'{e} Espinosa Msc,Phd.\\
%% Associate Professor \\
%% School of Electrical Engineering \\
%% Faculty of Mines \\
%% National University of Colombia - Medell\'{i}n Campus\\
%% Phone: +57 4 4255284 \\
%% E-mail: jairo.espinosa@ieee.org\\
%% \\  
%% Ing. John William Branch Msc,Phd.\\
%% Associate Professor \\
%% School of Systems  \\
%% Faculty of Mines \\
%% National University of Colombia - Medell\'{i}n Campus\\
%% Phone: +57 4 4255375 \\
%% E-mail: jwbranch@unalmed.edu.co\\
%% \\  
%% Ing. Andr\'{e}s Osorio Arias Msc,Phd.\\
%% Associate Professor \\
%% School of Geological and Environmental Sciences \\
%% Faculty of Mines \\
%% National University of Colombia - Medell\'{i}n Campus\\
%% Phone: +57 4 4255220 \\
%% E-mail: afosorioar@unal.edu.co\\
%% \\
%% Ing. Fernando Arango Isaza Msc,Phd.\\
%% Associate Professor \\
%% School of Systems  \\
%% Faculty of Mines \\
%% National University of Colombia - Medell\'{i}n Campus\\
%% Phone: +57 4 4255362 \\
%% E-mail: farango@unal.edu.co\\

%% \\  
%Ing. Esteban Salazar Guzman\\
%Software Analyst \\
%Susalud S.A. \\
%Phone:+57  4 4938320 \\
%Cell: +57 3003943091 \\
%E-mail: esalaza@gmail.com\\


%% Ing. Rafael Ignacio Larios\\
%% Software Analyst \\
%% Grupo Bancolombia S.A. \\
%% Phone: +57 4  \\
%% E-mail: esalaza@gmail.com\\
%% \\  


\end{resume}
\end{document}
